---
title: "Figures 1"
author: "Audrey Bahr"
date: "2/10/21"
output: html_notebook
---
```{r}
library(tidyverse)
library(cowplot)
library(glue)
library(colorspace)
```

3/29
```{r}
getwd()
setwd("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0")
getwd()
infect_cur_tot_0 <- read_csv("count_scenario_idx_0_current_symp_inf_Total.csv", col_names = TRUE)
# count_scenario_idx_0_current_symp_inf_Total.csv
```

```{r}
setwd("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0")
infect_cumul_tot_0 <- read_csv("count_scenario_idx_0_cumulative_symp_inf_Total.csv", col_names = TRUE)
```

(Automate this)
Load in all files for the different age groups

```{r}
file_name <- function(rate_count, s_num, cumul_curr, type, ag) {
  lab <- glue("{rate_count}_scenario_idx_{s_num}_{cumul_curr}_{type}_{ag}.csv")
  return(lab)
}
```


```{r}

  wd <- glue("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_{s_num}")
setwd(wd)
files <- list()
for (i in 1:12) {
  
  ag <- new_names[i+2]
  files[i] <- file_name(rate_count, s_num, cumul_curr, type, ag)
  
}

for (i in 1:12) {
  
  assign(paste0(type, cumul_curr, s_num, new_names[i+2]), read_csv(files[[i]], col_names = TRUE))
}


```

Add medians by rows
eg. for T files, add all medians for 2020-02-15

```{r}
t_median <- `infect018-25 T`$median + `infect026-49 T`$median + `infect050-64 T`$median + `infect065+ T`$median

s_median <- `infect018-25 S`$median + `infect026-49 S`$median + `infect050-64 S`$median + `infect065+ S`$median
  
x_median <- `infect018-25 X`$median + `infect026-49 X`$median + `infect050-64 X`$median + `infect065+ X`$median
```


New column - divide total by employment population (from Austin_pop)
(Calculate employment population first)
```{r}
t_pop <- sum(austin_pop$X18.25.T, austin_pop$X26.49.T, austin_pop$X50.64.T, austin_pop$X65..T)
  
s_pop <- sum(austin_pop$X18.25.S, austin_pop$X26.49.S, austin_pop$X50.64.S, austin_pop$X65..S)
  
x_pop <- sum(austin_pop$X18.25.X, austin_pop$X26.49.X, austin_pop$X50.64.X, austin_pop$X65..X)
```

```{r}
t_rate <- t_median / t_pop

s_rate <- s_median / s_pop

x_rate <- x_median / x_pop
```


Plot calculated rates on line graph. Rate vs date, colored by employment group.

```{r}
infect_0_plot <- data.frame(cbind(select(`infect018-25 S`, date), t_rate, s_rate, x_rate))

ggplot(infect_0_plot, aes(date, t_rate), color = "black") + geom_line() + geom_line(aes(date, s_rate), color = "blue") + geom_line(aes(date, x_rate), color = "red", size = .3)
```


Repeat

```{r}
rate_count <- "count"
s_num <- "0"
option <- "cumulative"
type <- "infections"

wd <- glue("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_{s_num}")
setwd(wd)
files <- list()
for (i in 1:12) {
  
  ag <- new_names[i+2]
  files[i] <- file_name(rate_count, s_num, option, type, ag)
  
}

for (i in 1:12) {
  
  assign(paste0(type, option, s_num, new_names[i+2]), read_csv(files[[i]], col_names = TRUE))
}
```

```{r}
t_rate <- (`symp_infcurrent218-25 T`$median + `symp_infcurrent226-49 T`$median + `symp_infcurrent250-64 T`$median + `symp_infcurrent265+ T`$median) / t_pop

s_rate <- (`symp_infcurrent218-25 S`$median + `symp_infcurrent226-49 S`$median + `symp_infcurrent250-64 S`$median + `symp_infcurrent265+ S`$median) / s_pop

x_rate <- (`symp_infcurrent218-25 X`$median + `symp_infcurrent226-49 X`$median + `symp_infcurrent250-64 X`$median + `symp_infcurrent265+ X`$median) / x_pop

sympinf_2_plot <- data.frame(cbind(select(`infect018-25 S`, date), t_rate, s_rate, x_rate))

ggplot(sympinf_2_plot, aes(date, x_rate, color = "Other")) + geom_line() + geom_line(aes(date, s_rate, color = "Staff")) + geom_line(aes(date, t_rate, color = "Teachers"), size = .3) + theme_minimal() + ggtitle("Rate of Infection", subtitle = "Symptomatic Individuals, Contact Reduction = 0.5") + xlab(NULL) + ylab("Rate") + scale_color_discrete_qualitative() + labs(color = "Employment Group") + guides(color = guide_legend(reverse=TRUE)) + scale_x_date(limits = c(as.Date("2020-02-15"), as.Date("2020-04-01"))) + theme(legend.position = "bottom")
```
sd = 0.5
```{r}
t_rate <- (`symp_infcurrent018-25 T`$median + `symp_infcurrent026-49 T`$median + `symp_infcurrent050-64 T`$median + `symp_infcurrent065+ T`$median) / t_pop

s_rate <- (`symp_infcurrent018-25 S`$median + `symp_infcurrent026-49 S`$median + `symp_infcurrent050-64 S`$median + `symp_infcurrent065+ S`$median) / s_pop

x_rate <- (`symp_infcurrent018-25 X`$median + `symp_infcurrent026-49 X`$median + `symp_infcurrent050-64 X`$median + `symp_infcurrent065+ X`$median) / x_pop


ggplot(sympinf_0_plot, aes(date, x_rate, color = "Other")) + geom_line() + geom_line(aes(date, s_rate, color = "Staff")) + geom_line(aes(date, t_rate, color = "Teachers"), size = .3) + theme_minimal() + ggtitle("Rate of Infection", subtitle = "Symptomatic Individuals, Contact Reduction = 0") + xlab(NULL) + ylab("Rate") + scale_color_discrete_qualitative() + labs(color = "Employment Group") + guides(color = guide_legend(reverse=TRUE)) + scale_x_date(limits = c(as.Date("2020-02-15"), as.Date("2020-04-01"))) + theme(legend.position = "bottom")
```
Why are the plots for scenario 0 and scenario 2 the same?



sd = 1
```{r}
t_rate <- (`symp_infcurrent418-25 T`$median + `symp_infcurrent426-49 T`$median + `symp_infcurrent450-64 T`$median + `symp_infcurrent465+ T`$median) / t_pop

s_rate <- (`symp_infcurrent418-25 S`$median + `symp_infcurrent426-49 S`$median + `symp_infcurrent450-64 S`$median + `symp_infcurrent465+ S`$median) / s_pop

x_rate <- (`symp_infcurrent418-25 X`$median + `symp_infcurrent426-49 X`$median + `symp_infcurrent450-64 X`$median + `symp_infcurrent465+ X`$median) / x_pop

sympinf_4_plot <- data.frame(cbind(select(`infect018-25 S`, date), t_rate, s_rate, x_rate))

ggplot(sympinf_4_plot, aes(date, x_rate, color = "Other")) + geom_line() + geom_line(aes(date, s_rate, color = "Staff")) + geom_line(aes(date, t_rate, color = "Teachers"), size = .3) + theme_minimal() + ggtitle("Rate of Infection", subtitle = "Symptomatic Individuals, Contact Reduction = 1") + xlab(NULL) + ylab("Rate") + scale_color_discrete_qualitative() + labs(color = "Employment Group") + guides(color = guide_legend(reverse=TRUE)) + scale_x_date(limits = c(as.Date("2020-02-15"), as.Date("2020-04-01")))
```
Cumulative Infections
```{r}
t_rate <- (`infectionscumulative018-25 T`$median + `infectionscumulative026-49 T`$median + `infectionscumulative050-64 T`$median + `infectionscumulative065+ T`$median) / t_pop

s_rate <- (`infectionscumulative018-25 S`$median + `infectionscumulative026-49 S`$median + `infectionscumulative050-64 S`$median + `infectionscumulative065+ S`$median) / s_pop

x_rate <- (`infectionscumulative018-25 X`$median + `infectionscumulative026-49 X`$median + `infectionscumulative050-64 X`$median + `infectionscumulative065+ X`$median) / x_pop

infcumul_0_plot <- data.frame(cbind(select(`infect018-25 S`, date), t_rate, s_rate, x_rate))

ggplot(infcumul_0_plot, aes(date, x_rate, color = "Other")) + geom_line() + geom_line(aes(date, s_rate, color = "Staff")) + geom_line(aes(date, t_rate, color = "Teachers"), size = .3) + theme_minimal() + ggtitle("Cumulative Rate of Infection", subtitle = "Symptomatic Individuals, Contact Reduction = 0") + xlab(NULL) + ylab("Rate") + scale_color_discrete_qualitative() + labs(color = "Employment Group") + guides(color = guide_legend(reverse=TRUE)) + scale_x_date(limits = c(as.Date("2020-02-15"), as.Date("2020-04-01")))
```

Adding child groups on.

```{r}
setwd("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0")
infectionscumulative004 <- read_csv("count_scenario_idx_0_cumulative_infections_0-4.csv", col_names = TRUE)
infectionscumulative0517 <- read_csv("count_scenario_idx_0_cumulative_infections_5-17.csv", col_names = TRUE)

```


```{r}
k1_rate <- infectionscumulative004$median / (austin_pop[1,3] + austin_pop[2,3])

k2_rate <- infectionscumulative0517$median / (austin_pop[1,4] + austin_pop[2,4])

infcumul_0_plot.2 <- cbind(infcumul_0_plot, k1_rate, k2_rate)

ggplot(infcumul_0_plot.2, aes(date, x_rate, color = "Other")) + geom_line() + geom_line(aes(date, s_rate, color = "Staff")) + geom_line(aes(date, t_rate, color = "Teachers")) + geom_line(aes(date, k1_rate, color = "Kids (0-4)")) + geom_line(aes(date, k2_rate, color = "Kids (5-17)")) + theme_minimal() + ggtitle("Cumulative Rate of Infection", subtitle = "Symptomatic Individuals, Contact Reduction = 0") + xlab(NULL) + ylab("Rate") + scale_color_discrete_qualitative() + labs(color = "Employment Group") + guides(color = guide_legend()) + scale_x_date(limits = c(as.Date("2020-02-15"), as.Date("2020-04-01")))
```

Check if time series data is identical
```{r}
identical(t_rate, s_rate)
identical(t_rate, x_rate)
identical(k1_rate, k2_rate)

identical(infectionscumulative004, infectionscumulative0517)
identical(`infectionscumulative018-25 S`, `infectionscumulative018-25 T`)
identical(`infectionscumulative018-25 X`, `infectionscumulative018-25 T`)
```
















2/10

```{r}
f <- file.choose()
hosp_current_total <- read_csv(f, col_names = TRUE)
```
```{r}
plot(hosp_current_total$date, hosp_current_total$sto_idx_0)
```


active parameters right now - sd level
  - infectiousness or susceptibility?
  - construction and UT Austin only had one age group
  - how to deal with a subgroup (teachers) spread over multiple age groups

Current hospitalizations vs Social distancing level
  - line plot - current
  - bar graph - cumulative
  - sto_idx_0 vs date
  - error bars: min, median, max
  - count scenario or rate scenario? - use rates, not counts
      - the other publications used counts?
  - colored by sd level

plots were Teachers and Staff

Import files
```{r}
tot_0_hcm <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/count_scenario_idx_0_cumulative_hospitalizations_Total.csv", col_names = TRUE)

tot_1_hcm <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_1/count_scenario_idx_1_cumulative_hospitalizations_Total.csv", col_names = TRUE)

tot_2_hcm <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_2/count_scenario_idx_2_cumulative_hospitalizations_Total.csv", col_names = TRUE)

tot_3_hcm <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_3/count_scenario_idx_3_cumulative_hospitalizations_Total.csv", col_names = TRUE)

tot_4_hcm <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_4/count_scenario_idx_4_cumulative_hospitalizations_Total.csv", col_names = TRUE)

```

```{r}
tot_hcm <- rbind(tot_0_hcm[nrow(tot_0_hcm),], tot_1_hcm[nrow(tot_1_hcm),], tot_2_hcm[nrow(tot_2_hcm),], tot_3_hcm[nrow(tot_3_hcm),], tot_4_hcm[nrow(tot_4_hcm),])

tot_hcm <- mutate(tot_hcm, sd_level = c("0", "0.25", "0.50", "0.75", "1"))
```

does a cumulative rate even make sense?
This is for "X" totals
```{r}
ggplot(tot_hcm, aes(sd_level, sto_idx_0)) + geom_col() + xlab("Level of Social Distancing") + ylab("Mid-August Cumulative Hospitalizations") + theme_half_open()
```

Fix, use color-blind friendly palette
```{r}
ggplot(tot_0_hcm, aes(date, sto_idx_0)) + geom_line(color = "red") + geom_line(data = tot_1_hcm, aes(date, sto_idx_0), color = "orange") + geom_line(data = tot_2_hcm, aes(date, sto_idx_0), color = "green") + geom_line(data = tot_3_hcm, aes(date, sto_idx_0), color = "blue") + geom_line(data = tot_4_hcm, aes(date, sto_idx_0), color = "black") + theme_half_open() + xlab("Date") + ylab("Cumulative Hospitalization Rate")
```

```{r}
# tot_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_Total.csv", col_names = TRUE)

t3_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_18-25 T.csv", col_names = TRUE)

t4_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_26-49 T.csv", col_names = TRUE)

t5_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_50-64 T.csv", col_names = TRUE)

t6_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_65+ T.csv", col_names = TRUE)
#---------------------------------------------------
x3_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_18-25 X.csv", col_names = TRUE)

x4_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_26-49 X.csv", col_names = TRUE)

x5_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_50-64 X.csv", col_names = TRUE)

x6_0_counth <- read_csv("/Users/audrey/Desktop/Current Projects/COVID/teacher_SEIR-master/outputs_test/scenario_idx_0/rate_scenario_idx_0_current_hospitalizations_65+ X.csv", col_names = TRUE)
```

linetype = 5
add legend

Teachers vs The Rest - not the way to go w/ cumulative
```{r}
ggplot() + geom_line(data = t3_0_counth, aes(date, sto_idx_0), color = "orange") + geom_line(data = t4_0_counth, aes(date, sto_idx_0), color = "green") + geom_line(data = t5_0_counth, aes(date, sto_idx_0), color = "blue") + geom_line(data = t6_0_counth, aes(date, sto_idx_0), color = "black") + geom_line(data = x3_0_counth, aes(date, sto_idx_0), color = "orange", linetype=5) + geom_line(data = x4_0_counth, aes(date, sto_idx_0), color = "green", linetype=5) + geom_line(data = x5_0_counth, aes(date, sto_idx_0), color = "blue", linetype=5) + geom_line(data = x6_0_counth, aes(date, sto_idx_0), color = "black", linetype=5) + theme_half_open() + xlab("Date") + ylab("Current Hospitalization Rate")
```

Staff vs X (same as above)


Infection Rates 
- T vs X
- S vs X

Death Rates 
- T vs X
- S vs X


```{r}

```

```{r}
ggplot(tot_hcm, aes(sd_level, sto_idx_0)) + geom_col() + xlab("Level of Social Distancing") + ylab("Cumulative Hospitalization Rate") + theme_half_open()
```

